---
output:
  pdf_document: default
  html_document: default
---
# Bin Review Data Management  
> This file uses the bin peer review data to make updates to the existing labels, create new bins and labels, and remove nonexistent bins and labels.  

\begin{center}\rule{3in}{0.4pt}\end{center}
## Data Formatting  
1. Initialization
```{r results='hide', error=F, warning=F, message=F}
# Init
if(!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("dkahle/ggmap", ref = "tidyup", force=TRUE)
library(tidyverse)
library(geojsonio)
library(sp)
library(ggmap)
library(sf)
library(geojsonsf)

# This is an API Key to use Google Maps in R. You can get one yourself from
# Google or ask me for mine. I didn't include it in the file because it
# costs money to use and I don't know who will see this file in the future
# - Oliver
ggmap::register_google("...")
```

2. Import GeoJSON
```{r}
# Parse GeoJSON
fileName = paste0(getwd(), '/geojson/review-combined.json')
geojsonText = readChar(fileName, file.info(fileName)$size)
sf <- geojson_sf(geojsonText)
```

3. Cleaning
  a. Remove duplicate bins based on ID  
```{r}
# Original n features
nrow(sf)
unique_bin_indices <- split(seq_along(sf$name), sf$name) %>% map_int(~ .[1])
sf_new <- sf[unique_bin_indices, ]
# New n features
nrow(sf_new)
```
  b. Tag for nonexistent bin
    - 1084FL
    - 1085FR
```{r}
non_ex_bin_indices <- which(sf_new$name %in% c('1084FL', '1085FR'))
sf_new <- sf_new[-non_ex_bin_indices, ]
# New n features
nrow(sf_new)
```
  c. Incorrect Bin Labels
```{r}
# New n features
nrow(sf_new)
# Zone 2
  # XL/XR -> IL/IR
sf_new[which(sf_new$name == '2007XR'), 'name'] <- '2xxxIR'
rm_1_df <- sf_new %>% filter(name == '2xxxIR')
rm_1_df[1, 'name'] <- '2xxxIL'
sf_new <- rbind(sf_new, rm_1_df)

sf_new[which(sf_new$name == '2010XL'), 'name'] <- '2010IL'
sf_new[which(sf_new$name == '2011XR'), 'name'] <- '2011IR'

sf_new[which(sf_new$name == '2009XL'), 'name'] <- '2009IL'
sf_new[which(sf_new$name == '2008XR'), 'name'] <- '2008IR'

sf_new[which(sf_new$name == '2003XL'), 'name'] <- '2003IL'
sf_new[which(sf_new$name == '2004XR'), 'name'] <- '2004IR'

  # F cluster -> D cluster
sf_new[which(sf_new$name == '2005FR'), 'name'] <- '2005DR'
sf_new[which(sf_new$name == '2006FL'), 'name'] <- '2006DL'
f_to_d_1 <- sf_new %>% filter(name == '2006DL')
f_to_d_1[1, 'name'] <- '2xxxDC'

sf_new[which(sf_new$name == '2066FR'), 'name'] <- '2066DR'
sf_new[which(sf_new$name == '2067FL'), 'name'] <- '2067DL'
f_to_d_2 <- sf_new %>% filter(name == '2067DL')
f_to_d_1[1, 'name'] <- '2xxxDC'

sf_new <- rbind(sf_new, f_to_d_1, f_to_d_2)

# Zone 3
sf_new[which(sf_new$name == '3027CC'), 'name'] <- '3027DC'
sf_new[which(sf_new$name == '3026CL'), 'name'] <- '3926DL'
sf_new[which(sf_new$name == '3025CR'), 'name'] <- '3025DR'

# New n features
nrow(sf_new)

# Extant Clusters
unique(substr(sf_new$name, 5, 5))
```
  d. No tag for existent bin  
```{r}
# Split by Zone
zone1_bins <- sf_new %>% filter(substr(name, 1, 1) == "1")
zone2_bins <- sf_new %>% filter(substr(name, 1, 1) == "2")
zone3_bins <- sf_new %>% filter(substr(name, 1, 1) == "3")
# Get Lat
zone1_bins_lat <- zone1_bins$geometry %>% map_dbl(~ .[2])
zone2_bins_lat <- zone2_bins$geometry %>% map_dbl(~ .[2])
zone3_bins_lat <- zone3_bins$geometry %>% map_dbl(~ .[2])
# Generate Bin ID xxx nums
zone1_bins$bin_num[order(zone1_bins_lat)] <- seq_along(zone1_bins_lat)
zone2_bins$bin_num[order(zone2_bins_lat)] <- seq_along(zone2_bins_lat)
zone3_bins$bin_num[order(zone3_bins_lat)] <- seq_along(zone3_bins_lat)
zone1_bins$bin_num <- formatC(zone1_bins$bin_num, width=3, flag="0")
zone2_bins$bin_num <- formatC(zone2_bins$bin_num, width=3, flag="0")
zone3_bins$bin_num <- formatC(zone3_bins$bin_num, width=3, flag="0")
# Get Streams
zone1_bins$stream_char <- substr(zone1_bins$name, 6, 6)
zone2_bins$stream_char <- substr(zone2_bins$name, 6, 6)
zone3_bins$stream_char <- substr(zone3_bins$name, 6, 6)
zone1_bins$stream <- zone1_bins$stream_char %>% recode(R="Recycle", C="Compost", L="Landfill")
zone2_bins$stream <- zone2_bins$stream_char %>% recode(R="Recycle", C="Compost", L="Landfill")
zone3_bins$stream <- zone3_bins$stream_char %>% recode(R="Recycle", C="Compost", L="Landfill")
# Generate Full Bin IDs
zone1_bins <- zone1_bins %>% mutate(new_name = paste0('1', bin_num, substr(name, 5, 6)))
zone2_bins <- zone2_bins %>% mutate(new_name = paste0('2', bin_num, substr(name, 5, 6)))
zone3_bins <- zone3_bins %>% mutate(new_name = paste0('3', bin_num, substr(name, 5, 6)))
# Recombine
sf_old <- sf_new
sf_new <- rbind(zone1_bins, zone2_bins, zone3_bins)
# Extant Clusters
unique(substr(sf_new$name, 5, 5))
```
  e. Reassigning X clusters
```{r}
# Zone 1
  # Behind Music School
    # N
sf_new[which(sf_new$new_name == '1185XR'), 'new_name'] <- '1185NR'
sf_new[which(sf_new$new_name == '1186XL'), 'new_name'] <- '1186NL'

sf_new[which(sf_new$new_name == '1189XR'), 'new_name'] <- '1189NR'
sf_new[which(sf_new$new_name == '1190XL'), 'new_name'] <- '1190NL'

sf_new[which(sf_new$new_name == '1194XR'), 'new_name'] <- '1194NR'
sf_new[which(sf_new$new_name == '1195XL'), 'new_name'] <- '1195NL'
    # M
sf_new[which(sf_new$new_name == '1196XL'), 'new_name'] <- '1196MR'
sf_new[which(sf_new$new_name == '1199XL'), 'new_name'] <- '1199ML'
  # YRL
    # L
sf_new[which(sf_new$new_name == '1160XL'), 'new_name'] <- '1160LL'
sf_new[which(sf_new$new_name == '1161XL'), 'new_name'] <- '1161LL'
sf_new[which(sf_new$new_name == '1162XL'), 'new_name'] <- '1162LL'
sf_new[which(sf_new$new_name == '1163XL'), 'new_name'] <- '1163LL'
  # Behind Powell
    # L
sf_new[which(sf_new$new_name == '1006XL'), 'new_name'] <- '1006LL'
sf_new[which(sf_new$new_name == '1007XL'), 'new_name'] <- '1007LL'
sf_new[which(sf_new$new_name == '1008XL'), 'new_name'] <- '1008LL'
sf_new[which(sf_new$new_name == '1009XL'), 'new_name'] <- '1009LL'
sf_new[which(sf_new$new_name == '1012XL'), 'new_name'] <- '1012LL'
sf_new[which(sf_new$new_name == '1013XL'), 'new_name'] <- '1013LL'
sf_new[which(sf_new$new_name == '1014XL'), 'new_name'] <- '1014LL'
sf_new[which(sf_new$new_name == '1018XL'), 'new_name'] <- '1018LL'
sf_new[which(sf_new$new_name == '1020XL'), 'new_name'] <- '1020LL'
  # Road behind Law
    # N
sf_new[which(sf_new$new_name == '1109XR'), 'new_name'] <- '1109NR'
sf_new[which(sf_new$new_name == '1104XL'), 'new_name'] <- '1104NL'

sf_new[which(sf_new$new_name == '1091XR'), 'new_name'] <- '1091NR'
sf_new[which(sf_new$new_name == '1090XL'), 'new_name'] <- '1090NL'

# Zone 2
  # Bruin Plaza
    # P
sf_new[which(sf_new$new_name == '2054XC'), 'new_name'] <- '2054PC'
sf_new[which(sf_new$new_name == '2055XR'), 'new_name'] <- '2055PR'
sf_new[which(sf_new$new_name == '2056XL'), 'new_name'] <- '2056PL'
  # Behind IM Field
    # N
sf_new[which(sf_new$new_name == '2140XR'), 'new_name'] <- '2140NR'
sf_new[which(sf_new$new_name == '2141XL'), 'new_name'] <- '2141NL'
sf_new[which(sf_new$new_name == '2142XL'), 'new_name'] <- '2142NL'
sf_new[which(sf_new$new_name == '2143XR'), 'new_name'] <- '2143NR'
sf_new[which(sf_new$new_name == '2145XL'), 'new_name'] <- '2145NL'
sf_new[which(sf_new$new_name == '2148XR'), 'new_name'] <- '2148NR'
  # Lab School 
    # M
sf_new[which(sf_new$new_name == '2160XL'), 'new_name'] <- '2160ML'
sf_new[which(sf_new$new_name == '2161XL'), 'new_name'] <- '2161ML'

# Zone 3
  # Kinsey
    # M
sf_new[which(sf_new$new_name == '3174XL'), 'new_name'] <- '3174ML'
  # Med
    # N
sf_new[which(sf_new$new_name == '3035XR'), 'new_name'] <- '3035NR'
sf_new[which(sf_new$new_name == '3036XL'), 'new_name'] <- '3036NL'
    # M
sf_new[which(sf_new$new_name == '3041XL'), 'new_name'] <- '3041ML'
sf_new[which(sf_new$new_name == '3081XL'), 'new_name'] <- '3081ML'
sf_new[which(sf_new$new_name == '3083XL'), 'new_name'] <- '3083ML'
sf_new[which(sf_new$new_name == '3084XL'), 'new_name'] <- '3084ML'
```

  f. Small Landfill  
  It turns out the all landfills in triple clusters are small, so we will make the `A` and `B` cluster contain `C`, `R`, `S` streams instead of `C`, `R`, `L`, in lieu of the small landfills.  
```{r}
small_landfills <- (sf_new %>% filter(substr(new_name, 5, 6) %in% c('BL', 'AL')))$new_name
for(bin_name in small_landfills) {
  sf_new[which(sf_new$new_name == bin_name), 'stream_char'] <- 'S'
  sf_new[which(sf_new$new_name == bin_name), 'new_name'] <- paste0(substr(bin_name, 1, 5), 'S')
}
```


## Export  
### GeoJSON  
#### Format  
```{r}
exportable_sf <- sf_new %>% transmute(Name=new_name, Stream=stream, 'Bin Number'=bin_num, 'Stream Character'=stream_char, Zone=substr(new_name, 1, 1))
```
#### Write File  
```{r, eval=F}
st_write(exportable_sf, dsn = paste0(getwd(), "/geojson/peer_reviewed_labels6.json"), driver = "GeoJSON")
```
### CSV  
#### Extra IDs  
1. M for every L and L for every M because they may be confused  
2. Extra bins in each zone in case of new bins
```{r}
# Ms & Ls
m_bins <- exportable_sf %>% filter(substr(Name, 5, 5) == 'M')
fake_l_bins <- m_bins %>% mutate(Name=paste0(substr(Name, 1, 4), 'L', substr(Name, 6, 6)))
fake_l_bins <- data.frame(Name=fake_l_bins$Name)

l_bins <- exportable_sf %>% filter(substr(Name, 5, 5) == 'L')
fake_m_bins <- l_bins %>% mutate(Name=paste0(substr(Name, 1, 4), 'M', substr(Name, 6, 6)))
fake_m_bins <- data.frame(Name=fake_m_bins$Name)

# Extra
unique_bin_chars <- unique(substr(exportable_sf$Name, 5, 6))
z1_max <- max(as.integer(exportable_sf$`Bin Number`[exportable_sf$Zone == '1']))
z2_max <- max(as.integer(exportable_sf$`Bin Number`[exportable_sf$Zone == '2']))
z3_max <- max(as.integer(exportable_sf$`Bin Number`[exportable_sf$Zone == '3']))
z1_extra <- character()
z2_extra <- character()
z3_extra <- character()
for(n in seq_along(unique_bin_chars)) {
  z1_extra <- c(z1_extra, paste0('1', as.character(z1_max + n), unique_bin_chars[n]))
}
for(n in seq_along(unique_bin_chars)) {
  z2_extra <- c(z2_extra, paste0('2', as.character(z1_max + n), unique_bin_chars[n]))
}
for(n in seq_along(unique_bin_chars)) {
  z3_extra <- c(z3_extra, paste0('3', as.character(z1_max + n), unique_bin_chars[n]))
}
z_extra_df <- data.frame(Name=c(z1_extra, z2_extra, z3_extra))

# I <3 REA
csv_bins_w_extra <- rbind(data.frame(Name=exportable_sf$Name), fake_l_bins, fake_m_bins, z_extra_df, data.frame(Name=rep('I <3 REA', 7)))
```
#### Write File
```{r, eval=F}
write_csv(csv_bins_w_extra, paste0(getwd(), "/label-order/FinalLabels2.csv"))
```



## Mapping
1. Formatting for mapping  
```{r, eval=F}
ilat <- sf_new$geometry %>% map_dbl(~ .[2])
ilong <- sf_new$geometry %>% map_dbl(~ .[1])
sf_new <- sf_new %>% mutate(lat=ilat, long=ilong)

x_clust <- sf_new %>% filter(substr(new_name, 5, 5) == 'X')
x_clust1 <- x_clust %>% filter(substr(new_name, 1,1) == '1')
x_clust2 <- x_clust %>% filter(substr(new_name, 1,1) == '2')
x_clust3 <- x_clust %>% filter(substr(new_name, 1,1) == '3')
```

```{r, eval=F}
# Base Terrain from Google
p <- ggmap(get_googlemap(center = c(Longitude = -118.442, Latitude = 34.06551),
                         zoom = 17, scale = 2,
                         maptype ='satellite',
                         color = 'color'))

p + geom_point(aes(x=long, y=lat, color=stream), data = x_clust3, size=2.5) 
x_clust3 %>% select(new_name, stream, lat, long) %>% arrange(lat)
```




















